Sulfur Dioxide on Water's Surface

### 2011-05-19 DensityResults.tex
reworked the results section. One overall results section with 3 different subsections.
Rewrote the surface density results section to take out the ambiguity regarding the model used

\section{Surface Density Distributions}

@@

In the neat-water slab, the \suldiox~molecular density distribution shows a surface affinity when in a low-concentration environment. It does not reside in the bulk or move out of the surface into the gas phase. This surface active behavior was found experimentally by the SFG study by our group,\cite{Tarbuck2005,Tarbuck2006} and also verified by the computational simulations and spectral calculations of Baer et al.\cite{Baer2010} The water behavior hypothesized from the experimental analysis is that a surface \suldiox~hydrate complex forms, modifying the structure of water above the Gibbs dividing surface (GDS). \wat~free-OH oscillators are thus shifted to stronger net orientation, creating a stronger hydrogen-bonding network, and resulting in an increase of the ``free-OH'' contribution to SFG signal intensity from the surface waters. In a later section of this article we look at the effect of \suldiox~on surface water orientation.

Both saturated \suldiox~surfaces exhibit accumulations of \suldiox. However, unlike the neat-water slab, the saturated slab has a non-zero bulk concentration of \suldiox~that does not adsorb to the surface. The added concentration of \suldiox~creates a layer of molecules bound to the top of the water surface. The center of the \suldiox~density distribution is further into the gas phase than for the neat-water surface with a single-\suldiox~molecule. The accumulation of \suldiox~in this classical simulation coincides with the experimental conclusions of \suldiox~surface hydrate complex formation. However, without simulating breakble bonds the chemistry that may pull \suldiox~into the bulk water phase, and the subsequent reaction to form ions is absent. We have confidence in the presence of surface complexation, the orienting effect of the \suldiox~on the surface water molecules, and the accumulation of \suldiox~at the interface. The specific geometries of the surface complexes, however, are not as well reproduced with the classical force-field as would be with ab initio methods.\cite{Baer2010} %However, we do not yet conclude that the specific locations of \suldiox~on top of the water surface are as accurate as those found in the DFT ab initio calculations of Baer et al.\cite{Baer2010} As was pointed out in their computations, the classical potential does not reproduce the bonding of the first hydration shell around \suldiox, and so conclusions about specific complex formation or geometries are best made from the ab initio simulation results reported.

>>>>

\subsection{Surface Density Distributions}

@@

In the simulated neat-water slab, the \suldiox~molecular density distribution indicates an affinity for the water surface. During the course of the simulation, the \suldiox~does not venture into the water bulk. Also, the \suldiox~does not escape the water surface into the gas phase, but remains located within 5-\angs~of the surface. This is consistent with what is found experimentally in our laboratory using VSFS,\cite{Tarbuck2005,Tarbuck2006} and also verified by the computational simulations and spectral calculations of Baer et al.\cite{Baer2010} The experimental studies indicated that upon exposure of \suldiox~to a \wat~surface, a layer of \suldiox~hydrate complex forms, modifying the structure of water above the Gibbs dividing surface (GDS). The \suldiox~bonding interaction with the free OH oscillators is manifested in a red-shift of the free OH frequency indicative of a bonding interaction. In a later section of this article we look at the effect of \suldiox~on surface water orientation.

The saturated surface simulation results indicate that under the high concentration conditions, \suldiox~accumulation at the surface is increased. However, unlike the neat-water slab, the saturated slab has a non-zero bulk concentration of \suldiox. The added concentration of \suldiox~creates a layer of molecules bound to the top of the water surface. The center of the \suldiox~density distribution is further into the gas phase than for the neat-water surface with a single-\suldiox~molecule. Because of the limitations of the classical model in accurately reproducing the first hydration shell around the \suldiox,\cite{Baer2010} we do not draw specific conclusions about the hydrate complex's geometry. However, the surface affinity of the hydrated \suldiox~is well reproduced by both the classical and ab initio methods, and is furthermore verified by our experimental results.

### 2011-05-19 Methods.tex
Rewrote the surface density results section to take out the ambiguity regarding the model used

        The location of the water surface was determined by the averaged positions of a set number of the outer-most waters in the simulated aqueous slabs. The number of waters included in the averaging was decided by taking a few issues into account. First, a visual inspection of the top cross-section of the water slab over several timesteps indicated between 65-75 waters established a full monolayer. Alternatively, assuming a spherical model of water with a radius of 2.2\angs~(the typical length of a bulk-water hydrogen bond), two layers of hexagonally tight-packed spheres would yield a similar number of molecules to the visual inspection. Increasing the number of waters used in calculating the surface location diminishes the effects of the few waters that briefly rise above the surface into the gas phase, stabilizing both the surface position and thickness values. Taking the close-packed model as a maximum number of waters fit into a flat surface, the authors decided to use 70 water molecules for calculating instantaneous water surface locations.

@@

	The simulated systems were analyzed to characterize the orientation of \wat~and \suldiox~in various environments above, within, and below the aqueous surface region. In order to better understand the chemistry occurring during the \suldiox~adsorption process, the molecular orientation of both the \wat~and \suldiox~must be understood.  The two molecules studied are similarly shaped with a C2$_v$ axis along their bisectors, and a molecular plane defined by three atoms. A body-fixed frame is defined for both \wat~and \suldiox~as shown in figure \ref{fig:molecular-frame}. In each analysis a space-fixed reference axis is used that corresponds to the long axis of the system's periodic cell normal to the plane of the water surface. The orientational analyses presented herein focus on two angles used to define molecular orientation. The molecular orientation angles $\theta$ and $\phi$ are determined from a set reference axis as shown in figure \ref{fig:water-angles}a.

>>>>

        The location of the water surface is determined by the averaged positions of a set number of the outer-most waters in the simulated aqueous slabs. The number of waters included in the averaging is determined by taking a few issues into account. First, a visual inspection of the top cross-section of the water slab over several timesteps indicated between 65-75 waters established a full monolayer. Alternatively, assuming a spherical model of water with a radius of 2.2\angs~(the typical length of a bulk-water hydrogen bond), two layers of hexagonally tight-packed spheres would yield a similar number of molecules to the visual inspection. Increasing the number of waters used in calculating the surface location diminishes the effects of the few waters that briefly rise above the surface into the gas phase, stabilizing both the surface position and thickness values. Taking the close-packed model as a maximum number of waters fit into a flat surface, the authors decided to use 70 water molecules for calculating instantaneous water surface locations.

@@

	The simulated systems were analyzed to characterize the orientation of \wat~and \suldiox~in various environments above, within, and below the aqueous surface region. The molecular orientation of both the \wat~and \suldiox~is a prerequisite for understanding the chemistry occurring during the \suldiox~adsorption process. The two molecules studied are similarly shaped with a C2$_v$ axis along their bisectors, and a molecular plane defined by three atoms. A body-fixed frame is defined for both \wat~and \suldiox~as shown in figure \ref{fig:molecular-frame}. In each analysis a space-fixed reference axis is used that corresponds to the long axis of the system's periodic cell normal to the plane of the water surface. The orientational analyses presented herein focus on two angles used to define molecular orientation. The molecular orientation angles $\theta$ and $\phi$ are determined from a set reference axis as shown in figure \ref{fig:water-angles}a.
